Survivable Set Connectivity

### 2015-05-08 draft.tex
made changes to rackes tree section

\subsection{Racke Tree Black Box}

We will use a particular type of tree embedding which will allow us to paths in the tree to paths in the graph.

\begin{definition}
For a given graph $G = (V, E)$, a Racke Tree is a tree embedding of $G$, $(T, y, \text{map})$ such that:
\begin{enumerate}
\item $\text{map}$ restricted to the leafs of $T$ is a bijection with the vertices of $G$.
\item For each edge $e \in E_t$ joining $u$ and $v$, $\text{map}(e)$ is a path joining nodes $\text{map}(u)$ and $\text{map}(v)$.
\item For some edge $e \in E_t$, $y_e$ (the cost of the edge) is a special quantity. Removing $y_e$ cuts the tree into two components, and so the leaves in the two components form a cut $\delta(S)$. Figure~\ref{fig:rackecut} gives an example for one such cut induced by an edge.
\begin{align}
y_e &= \sum_{e' \in \delta(S)} x_e
\end{align}
\end{enumerate}
\end{definition}

>>>>

\subsection{R\"{a}cke Tree Black Box}

We will use a particular type of tree embedding which will allow us to map paths in the tree to paths in the graph.

\begin{definition}
For a given graph $G = (V, E)$, a R\"{a}cke's Tree embedding is a triple of the form $(T,y,\mathrm{map})$ where $T = (V_T,E_T)$ is a rooted tree, $y$ is a capacity function on the edges $E_T$ of $T$, and $\mathrm{map}$ is a function $V_T \cup E_T \to V \cup 2^E$ satisfying the following properties:
\begin{enumerate}
\item $\mathrm{map}$ restricted to the leaves of $T$ is a bijection with the vertices of $G$. In other words, each leaf of the tree $T$ is in one-to-one correspondence with a vertex of the original graph, $G$.
\item For each edge $e \in E_T$ joining $u$ and $v$, $\text{map}(e)$ is a path joining nodes $\text{map}(u)$ and $\mathrm{map}(v)$.
\item For some edge $e \in E_T$, $y_e$ (the cost of the edge) is a special quantity. Removing $y_e$ cuts the tree into two components, and so the leaves in the two components form a cut $\delta(S)$. Figure~\ref{fig:rackecut} gives an example for one such cut induced by an edge.
\begin{align}
y_e &= \sum_{e' \in \delta(S)} x_e
\end{align}
\end{enumerate}
\end{definition}
